Signal Processing to Demodulate FM Radio

### 2020-12-13 doc/paper/paper.tex
update

  \subsection{Frequency Band}
    The frequency band that is used for FM sound broadcasting spans from 87.5 to 108 MHz in Europe. %https://www.itu.int/en/ITU-R/terrestrial/broadcast/Pages/FMTV.aspx
    This range is located within the so-called Very-High-Frequency (VHF) band.
    Anyone may use the specified frequency range freely, with a limited transmission power, as long as neighboring receivers are not disturbed in receiving an existing channel.
    Austria allowed the legal usage in 2006. %CHECK
    As an example, the German Federal Network Agency specifies the power limit as 50 nW, or -43 dBm, of effective radiated power (ERP).
    In a practical usecase, this means that a transmitter needs to select a channel that is not already occupied by an official sender.
    If a free channel is found, the transmitter may start sending a FM signal with the mentioned power limitations.
    %check Wikipedias' sources for my source references/links
    %https://www.conrad.at/de/o/fm-transmitter-1310051.html
    %https://de.wikipedia.org/wiki/FM-Transmitter
    %https://www.ris.bka.gv.at/GeltendeFassung.wxe?Abfrage=Bundesnormen&Gesetzesnummer=20008807
    %https://www.rtr.at/medien/was_wir_tun/frequenzverwaltung/Frequenzen.en.html

  \subsubsection{FM Channel Allocation}
    %each channel:
    % spacing
    % bandwidth
    % specific part of spectrum (see Fig.1)
    % TODO: make Fig1 smaller (cut top/bottom)
    \begin{figure}[!h]
      \centering
        \includegraphics[width=7cm]{img/fm-channel-freqs.png}
      \caption{Block diagram of the entire system.}
      \label{fig_sim}
    \end{figure}

>>>>

  \subsection{Frequency Band}
    The frequency band that is used for FM sound broadcasting spans from 87.5 to 108 MHz in Austria.
    This is also true worldwide, except that some countries only partially use the band. %http://search.itu.int/history/HistoryDigitalCollectionDocLibrary/1.43.48.en.101.pdf
    This range is located within the so-called Very-High-Frequency (VHF) band.
    Anyone may use the specified frequency range freely, with a limited transmission power, as long as neighboring receivers are not disturbed in receiving an existing channel.
    Austria allowed the legal usage in 2006. %CHECK
    As an example, the German Federal Network Agency specifies the power limit as 50 nW, or -43 dBm, of effective radiated power (ERP). %https://tech.ebu.ch/docs/r/r120.pdf
    In a practical usecase, this means that a transmitter needs to select a channel that is not already occupied by an official sender.
    If a free channel is found, the transmitter may start sending a FM signal with the mentioned power limitations.
    %check Wikipedias' sources for my source references/links
    %https://www.conrad.at/de/o/fm-transmitter-1310051.html
    %https://de.wikipedia.org/wiki/FM-Transmitter
    %https://www.ris.bka.gv.at/GeltendeFassung.wxe?Abfrage=Bundesnormen&Gesetzesnummer=20008807
    %https://www.rtr.at/medien/was_wir_tun/frequenzverwaltung/Frequenzen.en.html

  \subsubsection{FM Channel Allocation}
    %https://www.electronics-notes.com/articles/audio-video/broadcast-audio/vhf-fm-frequency-modulation-basics.php
    The entire FM band frequency range divides into multiple channels which can be used.
    In Europe, the European Telecommunications Standards Institute (ETSI) sets the respective standards for the usage of these frequencies.
    The main specifications for a single FM broadcasting channels are explained in this section.
    Each channel may allocate a bandwidth of 200 kHz.
    Within a channel, the maximum deviation from the center frequency shall not exceed 75 kHz.
    This leaves a guard band of 25 kHz on either side, to minimize interference with adjacent channels.
    Center frequencies may be allocated on multiples of 100 kHz.
    %each channel:
    % spacing
    % bandwidth
    % specific part of spectrum (see Fig.1)
    % TODO: make Fig1 smaller (cut top/bottom)
    \begin{figure}[!h]
      \centering
        \includegraphics[width=7cm]{img/fm-channel-baseband.png}
      \caption{Allocation of frequencies in an FM channel}
      \label{fig_sim}
    \end{figure}
